Versinus: an Animated Visualization Method for Evolving Networks\thanks{Supported by FAPESP}

### 2019-05-10 doc/paper.tex
escrito sobre os videos

>>>>

\subsection{Animations produced and available}\label{sec:vid}
Many animations were obtained through the routines described.
These encompassed different networks and settings ($\alpha$, $\sigma$, $\eta$,
etc), and different flavours of Versinus.
Some of these animations are available in six playlists of Youtube videos.
For organization and brevity, they are also available at~\cite{verRepo}.
